Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2024-03-21 experiments.tex
add metrics

\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
	\label{tab:bertall}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
		\cline{2-7} 
		\addlinespace
		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		TASE   & 60.28 & 55.59 & 65.83 & 78.16 & 78.27 & 78.06 \\ 
		LIQUID & 61.44 & 58.39 & 64.84 & 78.56 & 78.65 & 78.46 \\
		$\text{AUG}_{c}$ & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
		$\text{AUG}_{eree}$  & 63.93 & 60.22 & 68.13 & 77.50 & 77.07 & 77.94 \\
		$\text{AUG}_{ereec}$ & 62.90  & 61.02 & 64.89 & 76.72 & 78.56 & 74.97 \\
		Bagging & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
		\bottomrule
	\end{tabular*}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table*}

\begin{table*}[width=\textwidth,cols=8,pos=h]  
	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
	\label{tab:robertaall}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
		\cline{2-7} 
		\addlinespace
		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
		LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
		$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
		$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
		$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
		Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
		\bottomrule
	\end{tabular*}      
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table*}
Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID. These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer. 
Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics. However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.

@@

\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
	\caption{The statistics of answers span predicted by $\text{AUG}_{eree}$ and baselines} 
	\label{tab:answer_counts}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{ }} & \multicolumn{3}{c}{$\text{BERT}_{base}$} & \multicolumn{3}{c}{$\text{RoBERTa}_{base}$}  \\
		\cline{2-7} 
		\addlinespace
		& TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) & TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) \\
		\midrule
		empty predictions counts   & 0.0245 & 0.0214 & \textbf{0.0643} & 0.0061 & 0.0153 & \textbf{0.0291} \\ 
		non-empty Overlap f1  & 0.7964 & 0.7909 & \textbf{0.7976} & 0.8404 & 0.8357 & \textbf{0.8414} \\
		\bottomrule
	\end{tabular*}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table*}

@@

\begin{table*}[ht]
	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
	\label{tab:bertsub}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
		\cmidrule{3-8} 
		& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
		& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
		& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
		& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
		& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
		& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
		\midrule
		\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
		& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
		& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
		& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
		& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
		& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
		\midrule
		\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
		& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
		& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
		& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
		& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
		& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
		\bottomrule
	\end{tabular*}
\end{table*}

\begin{table*}[ht]
	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
	\label{tab:robertasub}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
		\cmidrule{3-8} 
		& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
		& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
		& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
		& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
		& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
		& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
		\midrule
		\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
		& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
		& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
		& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
		& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
		& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
		\midrule
		\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
		& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
		& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
		& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
		& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
		& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
		\bottomrule
	\end{tabular*}
\end{table*}

>>>>

\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
	\label{tab:bertall}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
		\cline{2-7} 
		\addlinespace
		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		TASE   & 60.28 & 55.59 & 65.83 & 78.16 & 78.27 & 78.06 \\ 
		LIQUID & 61.44 & 58.39 & 64.84 & 78.56 & 78.65 & 78.46 \\
		$\text{AUG}_{c}$ & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
		$\text{AUG}_{eree}$  & 63.93 & 60.22 & 68.13 & 77.50 & 77.07 & 77.94 \\
		$\text{AUG}_{ereec}$ & 62.90  & 61.02 & 64.89 & 76.72 & 78.56 & 74.97 \\
		$\text{Bagging}_{eeerc}$ & 63.63  & 61.53 & 65.88 & 78.24 & 80.00 & 76.56 \\
		$\text{Bagging}_{eeerc+liquid}$ & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
		\bottomrule
	\end{tabular*}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table*}

\begin{table*}[width=\textwidth,cols=8,pos=h]  
	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
	\label{tab:robertaall}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
		\cline{2-7} 
		\addlinespace
		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
		LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
		$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
		$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
		$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
		$\text{Bagging}_{eeerc}$ & 70.48  & 69.11 & 71.90 & 84.28 & 85.61 & 83.00 \\
		$\text{Bagging}_{eeerc+liquid}$ & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
		\bottomrule
	\end{tabular*}      
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table*}
Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID. These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer. 
Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics. However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.

@@

\begin{table}[htbp]
	\caption{The statistics of answers span predicted by $\text{AUG}{eree}$, $\text{AUG}{ereec}$ and baselines}
	\label{tab:answer_counts_vertical}
	\centering
	\begin{tabular}{lcc}
		\toprule
		\textbf{Category} & \textbf{BERT} & \textbf{RoBERTa} \\
		\midrule
		\multicolumn{3}{l}{\textbf{TASE}} \\
		\hspace{5mm} empty preds & 2.45 & 0.61 \\
		\hspace{5mm} non-empty pmf1 & 79.64 & 84.04 \\
		\multicolumn{3}{l}{\textbf{LIQUID)}} \\
		\hspace{5mm} empty preds & 2.14 & 1.53 \\
		\hspace{5mm} non-empty pmf1 & 79.09 & 83.57 \\
		\multicolumn{3}{l}{$\textbf{AUG}{eree}$ } \\
		\hspace{5mm} empty preds & \textbf{6.43} & \textbf{2.91} \\
		\hspace{5mm} non-empty pmf1 & \textbf{79.76} & \textbf{84.14} \\
		\multicolumn{3}{l}{$\textbf{AUG}{ereec}$ } \\
		\hspace{5mm} empty preds & \textbf{7.96} & \textbf{3.22} \\
		\hspace{5mm} non-empty pmf1 & \textbf{80.20} & \textbf{83.78} \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table*}[ht]
	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
	\label{tab:bertsub}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
		\cmidrule{3-8} 
		& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
		& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
		& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
		& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
		& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
		& $\text{Bagging}_{eeerc}$ & 39.19  & 36.86 & 41.83 & 64.46 & 75.12 & 56.45 \\
		& $\text{Bagging}_{eeerc+liquid}$  & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
		\midrule
		\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
		& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
		& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
		& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
		& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
		& $\text{Bagging}_{eeerc}$ & 35.58 & 35.92 & 35.24 & 58.62  & 68.09 & 51.46 \\
		& $\text{Bagging}_{eeerc+liquid}$  & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
		\midrule
		\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
		& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
		& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
		& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
		& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
		& $\text{Bagging}_{eeerc}$ & 68.68  & 66.49 & 71.03 & 81.11 & 81.39 & 80.83 \\
		& $\text{Bagging}_{eeerc+liquid}$ & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
		\bottomrule
	\end{tabular*}
\end{table*}

\begin{table*}[ht]
	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
	\label{tab:robertasub}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
		\toprule
		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
		\cmidrule{3-8} 
		& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
		& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
		& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
		& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
		& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
		& $\text{Bagging}_{eeerc}$ & 51.54 & 47.56 & 56.25 & 78.20 & 80.04 & 76.44 \\
		& $\text{Bagging}_{eeerc+liquid}$ & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
		\midrule
		\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
		& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
		& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
		& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
		& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
		& $\text{Bagging}_{eeerc}$ & 43.32 & 41.96 & 44.76 & 68.57 & 76.54 & 62.11 \\
		& $\text{Bagging}_{eeerc+liquid}$ & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
		\midrule
		\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
		& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
		& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
		& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
		& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
		& $\text{Bagging}_{eeerc}$ & 74.97 & 74.23 & 75.72 & 86.14 & 87.07 & 87.06 \\
		&$\text{Bagging}_{eeerc+liquid}$ & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
		\bottomrule
	\end{tabular*}
\end{table*}
